---
date: "2019-05-05T00:00:00+01:00"
title: "Databases for metID"
linktitle: "1 Databases for metID"
author: admin
type: book
weight: 1
commentable: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
knitr::opts_knit$set(root.dir = here::here("content/docs"))
```


## Introduction

The database class in `metid` is `databaseClass`. You can use the demo database in `metid` to explore it.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
library(metid)
data("snyder_database_rplc0.0.3")
snyder_database_rplc0.0.3
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
class(snyder_database_rplc0.0.3)
```

It contains three parts:

1. spectra.info: The information for all the metabolites/compounds in the database.

```{r,eval=TRUE, echo=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
library(kableExtra)
library(magrittr)
kbl(snyder_database_rplc0.0.3@spectra.info) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "600px")
```

2. database.info: The information of the database.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
snyder_database_rplc0.0.3@database.info
```

3. spectra.data: The spectra of the metabolites in database.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
names(snyder_database_rplc0.0.3@spectra.data)
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
head(names(snyder_database_rplc0.0.3@spectra.data$Spectra.positive))
```

One metabolite may contains multiple spectra.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
snyder_database_rplc0.0.3@spectra.data$Spectra.positive$RPLC_1$NCE25
```

You can use [the function from masstools](https://masstools.tidymass.org/reference/ms2_plot) to visualize the ms2 spectra.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
if(!require(masstools)){
  remotes::install_gitlab("tidymass/masstools")
}
library(masstools)
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
ms2_plot(
  snyder_database_rplc0.0.3@spectra.data$Spectra.positive$RPLC_1$NCE25
)
```

## Extract spectra from database

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
ms2 <-
  get_ms2_spectrum(lab.id = "RPLC_1", 
                   database = snyder_database_rplc0.0.3,
                   polarity = "positive", 
                   ce = "NCE25"
                    )
ms2
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
ms2_plot(ms2)
```

## Convert `databaseClass` to other database format

[`MassBank`](https://massbank.eu/), [`MoNA`](https://mona.fiehnlab.ucdavis.edu/) and some other public databases provide `msp` format database of metabolites. So you can use the functions in `metid` to output `metid` format database to `msp` format which can be used for `GNPS`, `MassBank` and `MoNA`.

### MassBank

#### `msp` format

Just use the `write_msp_massbank()` function to output `metid` database to `msp` format for MassBank.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
write_msp_massbank(databasae = databasae, path = ".")
```

The arguments of `write_msp_massbank()` can be found using `?write_msp_massbank()`.

#### `mgf` format

Just use the `write_mgf_massbank()` function to output `metid` database to `mgf` format for MassBank.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
write_mgf_massbank(databasae = databasae, path = ".")
```

The arguments of `write_msp_massbank()` can be found using `?write_msp_massbank()`.

### MoNA

#### `msp` format

Just use the `write_msp_mona()` function to output `metid` database to `msp` format for mona.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
write_msp_mona(databasae = databasae, path = ".")
```

The arguments of `write_msp_mona()` can be found using `?write_msp_mona()`.

#### `mgf` format

Just use the `write_mgf_mona()` function to output `metid` database to `mgf` format for mona.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
write_mgf_mona(databasae = databasae, path = ".")
```

The arguments of `write_msp_mona()` can be found using `?write_msp_mona()`.

### GNPS

#### `msp` format

Just use the `write_msp_gnps()` function to output `metid` database to `msp` format for gnps.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
write_msp_gnps(databasae = databasae, path = ".")
```

The arguments of `write_msp_gnps()` can be found using `?write_msp_gnps()`.

#### `mgf` format

Just use the `write_mgf_gnps()` function to output `metid` database to `mgf` format for gnps.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
write_mgf_gnps(databasae = databasae, path = ".")
```

The arguments of `write_msp_gnps()` can be found using `?write_msp_gnps()`.

## Session information

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
sessionInfo()
```
