---
date: "2019-05-05T00:00:00+01:00"
title: "Add MS2 spectra data into mass_dataset class object"
linktitle: "2 Add MS2 spectra"
author: admin
type: book
weight: 2
commentable: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
knitr::opts_knit$set(root.dir = here::here("content/docs"))
```

`mass_dataset` class object can also contain MS2 data. 

## Data preparation

### `mass_dataset` class object

We need to create a `mass_dataset` class object first, [see this document](../../chapter2/1-create_mass_dataset/). And here we use the data from this step as an example.

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
load("feature_table/object_pos")
load("feature_table/object_neg")
```

### MS2 data

The MS2 raw data should be converted to `mgf` format data. Please [refer this document](../../chapter3/1-data_convert/).

Here we use the demo data for `tidymass`, please download it and put it in the `mgf_ms2_data` folder.

[💾 Download link is here.](https://drive.google.com/file/d/1FY3x7q5i1g3oSLaVej__ZaZ4XSX-mWBQ/view?usp=sharing)

Then uncompress it.

## Add MS2 to `mass_dataset` class object

Positive mode.

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
library(massdataset)
object_pos2 =
  mutate_ms2(
    object = object_pos,
    column = "rp",
    polarity = "positive",
    ms1.ms2.match.mz.tol = 10,
    ms1.ms2.match.rt.tol = 15,
    path = "mgf_ms2_data/POS/"
  )
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
object_pos2
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
object_pos2@ms2_data
```

Negative mode.

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
object_neg2 =
  mutate_ms2(
    object = object_neg,
    column = "rp",
    polarity = "negative",
    ms1.ms2.match.mz.tol = 10,
    ms1.ms2.match.rt.tol = 15,
    path = "mgf_ms2_data/NEG/"
  )
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
object_neg2@ms2_data
```

## Session information

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```
