---
date: "2019-05-05T00:00:00+01:00"
title: "Create mass_dataset class from other tools"
linktitle: "3 Create mass_dataset class from other tools"
author: admin
type: book
weight: 3
commentable: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
knitr::opts_knit$set(root.dir = here::here("content/docs"))
```


If you don't want to use the `massprocesser` for raw data processing, you can absolutely use other tools (mzMine or MS-DIAL). Then you can just use the functions from `massdataset` convert results from them to `mass_dataset` class.

## mzMine feature table to `mass_dataset` class

We can also directory convert feature table from [mzMine](http://mzmine.github.io/) to `mass_dataset` class.

An example feature table from mzMine.

```{r,eval=TRUE, echo=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
library(massdataset)
data("mzmine_table")
library(kableExtra)
library(magrittr)
kbl(mzmine_table[1:30,]) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "600px")
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data("mzmine_table")
object =
   convet_mzmine2mass_dataset(x = mzmine_table)
object
```

## MS-DIAL feature table to `mass_dataset` class

We can also directory convert feature table from [MS-DIAL](http://prime.psc.riken.jp/compms/msdial/main.html) to `mass_dataset` class.

An example feature table from MS-DIAL.

```{r,eval=TRUE, echo=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
library(massdataset)
data("msdial_table")
library(kableExtra)
library(magrittr)
kbl(msdial_table[1:30,]) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "600px")
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data("msdial_table")
object =
   convert_msdial2mass_dataset(x = msdial_table)
object
```

## Session information

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```